---
title: " "		
output:
  pdf_document:
    pandoc_args: !expr acronymsdown::add_filter()
    number_sections: TRUE
    # citation_package: natbib

    # pandoc_args: ['--lua-filter=section-bibliographies.lua.txt']
    # pandoc_args: ['--lua-filter=multibib.lua']
  # word_document:
  #   pandoc_args: !expr acronymsdown::add_filter()
  #   number_sections: TRUE
    
reference-section-title: Works Cited

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}
  # - \usepackage{acro}
  # - \usepackage{float}
  # - \usepackage{chapterbib}
  # - \usepackage{lastpage}
  # - \usepackage{dcolumn}
  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
  # - \addbibresource{bibliography.bib}  
  
bibliography: main.bib
# natbiboptions: "numbers"
csl: https://www.zotero.org/styles/the-lancet 

  # intro: intro.bib
  # ch1: chapter1.bib
  # 

acronyms:
  insert_loa: false
  loa_title: ""

  # loa_title: "List of Acronyms"
  keys:
    - shortname: LMIC
      longname: low and middle income country

---


```{r setup0, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE) 
library(acronymsdown)
```

\allsectionsfont{\centering\normalsize}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{roman}
\pagestyle{empty}

\begin{centering}

\vspace*{36pt}

\large

{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}

\vspace{12pt}

\normalsize

by

\vspace{12pt}

{\ Daniel Alejandro Arias}

\vspace{36pt}

A dissertation submitted to the faculty of \\
the Harvard T.H. Chan School of Public Health\\
in partial fulfillment of the requirements\\
for the degree of \emph{Doctor of Philosophy}\\
in the Department of Global Health and Population

\vspace{42pt}

Harvard University \\
Cambridge, Massachusetts

\vspace{42pt}

`r format(Sys.time(), '%B %Y')`

\end{centering}

\newpage

\vspace*{\fill}
© `r format(Sys.time(), '%Y')` Daniel Arias. All rights reserved.

\newpage

\pagestyle{plain}

\normalsize

\begin{centering}

Dissertation Advisor: Stéphane Verguet \hfill Daniel Arias

\vspace{24 pt}

{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}

\vspace{12pt}

\section*{Abstract}

\addcontentsline{toc}{section}{Abstract}

\end{centering}

We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020. On November 9^th^, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16^th^, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S. Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.


This is a \acr{LMIC}. This is also a \acr{LMIC}.

Augue eget arcu dictum varius duis at. Tempor orci eu lobortis elementum nibh. Nibh sit amet commodo nulla. At varius vel pharetra vel. In metus vulputate eu scelerisque felis imperdiet. Venenatis tellus in metus vulputate eu. Aliquam sem fringilla ut morbi tincidunt augue. Risus feugiat in ante metus dictum at tempor commodo ullamcorper. In dictum non consectetur a erat nam. Ut sem viverra aliquet eget sit. Eleifend donec pretium vulputate sapien nec sagittis aliquam. Neque viverra justo nec ultrices dui. Turpis in eu mi bibendum neque egestas. Tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla facilisi.

Augue eget arcu dictum varius duis at. Tempor orci eu lobortis elementum nibh. Nibh sit amet commodo nulla. At varius vel pharetra vel. In metus vulputate eu scelerisque felis imperdiet. Venenatis tellus in metus vulputate eu. Aliquam sem fringilla ut morbi tincidunt augue. Risus feugiat in ante metus dictum at tempor commodo ullamcorper. In dictum non consectetur a erat nam. Ut sem viverra aliquet eget sit. Eleifend donec pretium vulputate sapien nec sagittis aliquam. Neque viverra justo nec ultrices dui. Turpis in eu mi bibendum neque egestas. Tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla facilisi.

\cleardoublepage

\begin{spacing}{1}

\renewcommand*\contentsname{Table of Contents}

\tableofcontents

\addcontentsline{toc}{section}{Table of Contents}

\newpage

\listoffigures

\newpage

\listoftables

\newpage

\cleardoublepage

\end{spacing}

```{r frontmatter, child='frontmatter.Rmd'}
```

\cleardoublepage

\pagenumbering{arabic}

```{r intro, child='intro.Rmd'}
```


\cleardoublepage

```{r paper1, child='paper1.Rmd'}
```


\cleardoublepage

```{r paper2, child='paper2.Rmd'}
```

\cleardoublepage

```{r paper3, child='paper3.Rmd'}
```

<!-- \newpage -->

<!-- ```{r conclusion, child='conclusion.Rmd'} -->
<!-- ``` -->

<!-- \cleardoublepage -->

<!-- \section*{References} -->

<!-- \addcontentsline{toc}{section}{References} -->

<!-- <div id="refs"></div> -->

<!-- \cleardoublepage -->

<!-- \section*{Supplementary materials} -->

<!-- \addcontentsline{toc}{section}{Supplementary materials} -->

<!-- ```{r appendix_all, child='appendix.Rmd'} -->
<!-- ``` -->

<!-- \newpage -->


```{r todo}

### TO DO / KNOWN ISSUES

# Acronyms with acronym down
# Separate bibliography for each section
# Numbered figures and tables by section

# Check that sequential articles are represented by a dash
# Table of figures and tables
# Institutional authors need to be fixed in bibliography

```

